Forcing for Isabelle

### 2018-12-14 LICS/easy-axioms.tex
precisando comentarios
Descripción corta de locales (copiado de Whatsapp)

\fbox{Hablar de \texttt{M\_trivial}}

\fbox{Falta check(x) para Infinity}

>>>>

It is straightforward to show that the generic extension $M[G]$
satisfies foundation, union, and infinity. The easiest one is
foundation which does not depend on the satisfaction by $M$.

\fbox{Hablar de \texttt{M\_trivial} y del uso de interfaz para instanciar}

\fbox{Falta \texttt{check\_in\_M} para completar Infinity}
